---
title: "Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

This package theme is derived from a dataset of wine enthusiast ratings used to provide users (wine buyers) with purchase decisions that maximize satisfaction/cost. This dataset is provided by Kaggle and it can be found [*here*](https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-28/winemag-data-130k-v2.csv).

This vignette shows you how to see the average points and average prices of wines from different countries, calls a function that shows a box plot about the relationship between wine prices and points, calls a function that shows a wordcloud plot about the wine descriptions, and launches my shiny app using the **wine** package.

Load the `wine` package using the `library()` function. 

```{r setup}
library(dplyr)
library(ggplot2)
library(maps)
library(RColorBrewer)
library(wine)
```

# Data Description

In order to use the functions in the **wine** package, a built-in dataset `wine` is required.

The dataset "wine" contains only four of the variables: country, points, price and description.

```{r}
str(wine::wine)
```
For more details about this dataset, you can use the function `?wine::wine`

# Wine point and price

**`point_price()` is the main function of `wine` package. 

## Example

You can enter a country name directly into the function to see the average point and average price for that country's wines.

```{r}
point_price("US")
```

If you enter an incorrect country or if the dataset does not contain data for that country, the following prompt will appear:

```{r}
point_price("world")
```

## Data Overview

To more accurately visualize the average wine point rankings for each country, I use the `map_data` dataset to create a world map of the average wine points for each country.

```{r}
wine %>% 
  filter(!is.na(country)) %>%
  group_by(country) %>%
  summarise(mean = mean(points, na.rm = TRUE),
            total_wine = n()) %>%
  right_join(map_data("world"),
             by = c("country" = "region")) %>%
  ggplot(mapping = aes(x = long,
                       y = lat,
                       group = group)) +
  geom_polygon(aes(fill = mean)) +
  scale_fill_continuous(low = "#9DBF9E",
                        high = "darkred",
                        na.value = "snow2") +
  coord_map(xlim = c(-180, 180),
            ylim = c(-60, 80)) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_rect(fill = "white"))
```

The map shows that some European countries produce wines that are favored, and that Canada, India, China and Australia have good average points for their wines.

# Wine Box Plot

**`boxPlot()` is the main function of `wine` package. 

## Example

You can see the box plot of wine points and prices for each country by typing the name of the country into the function.

```{r}
boxPlot("Australia")
```

If you enter an incorrect country or if the dataset does not contain data for that country, `boxPlot()` will draw a box plot with the points and prices of wine for all countries as data, it will look like this:

```{r}
boxPlot("au")
```

For more details about this function, you can use the function `?wine::boxPlot`

# Wine wordcloud plot

**`wordcloud()` is the main function of `wine` package.

## Example

You can type a country into the function and it will draw a wordcloud plot about wine descriptions for this country.

```{r}
wordcloud("Canada")
```

If you enter an incorrect country or if the dataset does not contain data for that country, `wordcloud()` will draw a wordcloud plot with all wine descriptions.

For more details about this function, you can use the function `?wine::wordcloud`

# Wine shiny app

**`myapp()` is a function of `wine` package. 

## Example

You can view the shiny app on the wine dataset by directly running the following code, which includes point plot, column plot, box plot and wordcloud, which will help you to understand the information about wine points, prices and descriptions in the *wine* dataset.

```{r, eval = FALSE}
myapp()
```

For more details about this function, you can use the function `?wine::myapp`
